---
title: "AirbnbSentimentAnalysis"
author: "Kiana"
date: "7/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages

```{r loadPackages, echo=FALSE}
library(twitteR)
library(ROAuth)
library(hms)
library(lubridate) 
library(tidytext)
library(textdata)
library(tm)
library(wordcloud)
library(igraph)
library(glue)
library(networkD3)
library(rtweet)
library(plyr)
library(stringr)
library(ggplot2)
library(ggeasy)
library(plotly)
library(dplyr)  
library(hms)
library(lubridate) 
library(magrittr)
library(tidyverse)
library(janeaustenr)
library(widyr)
library(Rcpp)
```

## Pull airbnb tweets

You can also embed plots, for example:

```{r pullTweets}
#Note: Replace below with your credentials following above reference
api_key <- "api_key"
api_secret <- "api_secret_key"
access_token <- "access_token"
access_token_secret <- "access_secret_token"

#Note: This will ask us permission for direct authentication, type '1' for yes:
setup_twitter_oauth(api_key,api_secret,access_token,access_token_secret)

# extracting 5000 tweets related to Airbnb
tweets <- searchTwitter("Airbnb -filter:retweets", n=5000, lang="en")
n.tweet <- length(tweets)

# convert tweets to a data frame
tweets.df <- twListToDF(tweets)

tweets.txt <- sapply(tweets, function(t)t$getText())
# Ignore graphical Parameters to avoid input errors
tweets.txt <- str_replace_all(tweets.txt,"[^[:graph:]]", " ")

#save the tweets
write.csv(tweets.df,"AirbnbTweets.csv")
```

## Pre-processing

```{r preProcessTweets}
clean.text = function(x)
{
  # convert to lower case
  x = tolower(x)
  # remove rt
  x = gsub("rt", "", x)
  # remove at
  x = gsub("@\\w+", "", x)
  # remove punctuation
  x = gsub("[[:punct:]]", "", x)
  # remove numbers
  x = gsub("[[:digit:]]", "", x)
  # remove links http
  x = gsub("http\\w+", "", x)
  # remove tabs
  x = gsub("[ |\t]{2,}", "", x)
  # remove blank spaces at the beginning
  x = gsub("^ ", "", x)
  # remove blank spaces at the end
  x = gsub(" $", "", x)
  # some other cleaning text
  x = gsub('https://','',x)
  x = gsub('http://','',x)
  x = gsub('[^[:graph:]]', ' ',x)
  x = gsub('[[:punct:]]', '', x)
  x = gsub('[[:cntrl:]]', '', x)
  x = gsub('\\d+', '', x)
  x = str_replace_all(x,"[^[:graph:]]", " ")
  return(x)
}

cleanText <- clean.text(tweets.txt)
# remove empty results (if any)
idx <- which(cleanText == " ")
cleanText <- cleanText[cleanText != " "]

# frequency of tweets
tweets.df %<>% 
  mutate(
    created = created %>% 
      # Remove zeros.
      str_remove_all(pattern = '\\+0000') %>%
      # Parse date.
      parse_date_time(orders = '%y-%m-%d %H%M%S')
  )

tweets.df %<>% 
  mutate(Created_At_Round = created%>% round(units = 'hours') %>% as.POSIXct())

tweets.df %>% pull(created) %>% min()

tweets.df %>% pull(created) %>% max()
```

## Number of tweets per hour

Plot the number of tweets per hour.

```{r TweetsPerHour}
# plot number of tweets per hour
plt <- tweets.df %>% 
  dplyr::count(Created_At_Round) %>% 
  ggplot(mapping = aes(x = Created_At_Round, y = n)) +
  theme_light() +
  geom_line() +
  xlab(label = 'Date') +
  ylab(label = NULL) +
  ggtitle(label = 'Number of Tweets per Hour')

plt %>% ggplotly()
```

## Sentiment Scoring

Assign a score
```{r SentimentScoring}
# load sentiment analysis words
positive = scan('positive-words.txt', what = 'character', comment.char = ';')
negative = scan('negative-words.txt', what = 'character', comment.char = ';')

# add your list of words below as you wish if missing in above read lists
pos.words = c(positive,'upgrade','Congrats','prizes','prize','thanks','thnx',
              'Grt','gr8','plz','trending','recovering','brainstorm','leader')
neg.words = c(negative,'wtf','wait','waiting','epicfail','Fight','fighting',
              'arrest','no','not')

# sentiment scoring function
score.sentiment = function(sentences, pos.words, neg.words, .progress='none')
{
  require(plyr)
  require(stringr)
  
  # we are giving vector of sentences as input. 
  # plyr will handle a list or a vector as an "l" for us
  # we want a simple array of scores back, so we use "l" + "a" + "ply" = laply:
  scores = laply(sentences, function(sentence, pos.words, neg.words) {
    
    # clean up sentences with R's regex-driven global substitute, gsub() function:
    sentence = gsub('https://','',sentence)
    sentence = gsub('http://','',sentence)
    sentence = gsub('[^[:graph:]]', ' ',sentence)
    sentence = gsub('[[:punct:]]', '', sentence)
    sentence = gsub('[[:cntrl:]]', '', sentence)
    sentence = gsub('\\d+', '', sentence)
    sentence = str_replace_all(sentence,"[^[:graph:]]", " ")
    # and convert to lower case:
    sentence = tolower(sentence)
    
    # split into words. str_split is in the stringr package
    word.list = str_split(sentence, '\\s+')
    # sometimes a list() is one level of hierarchy too much
    words = unlist(word.list)
    
    # compare our words to the dictionaries of positive & negative terms
    pos.matches = match(words, pos.words)
    neg.matches = match(words, neg.words)
    
    # match() returns the position of the matched term or NA
    # we just want a TRUE/FALSE:
    pos.matches = !is.na(pos.matches)
    neg.matches = !is.na(neg.matches)
    
    # TRUE/FALSE will be treated as 1/0 by sum():
    score = sum(pos.matches) - sum(neg.matches)
    
    return(score)
  }, pos.words, neg.words, .progress=.progress )
  
  scores.df = data.frame(score=scores, text=sentences)
  return(scores.df)
}

# calculate sentiment score
analysis <- score.sentiment(cleanText, pos.words, neg.words)
```

Look at sentiment score frequency

```{r sentimentScoreFrequency}
table(analysis$score)
```

Histogram of sentiment scores

```{r sentimentScoreHistogram}
analysis %>%
  ggplot(aes(x=score)) + 
  geom_histogram(binwidth = 1, fill = "lightblue")+ 
  ylab("Frequency") + 
  xlab("sentiment score") +
  ggtitle("Distribution of Sentiment scores of the tweets") +
  ggeasy::easy_center_title()
```
Analysis: a majority of the comments were labeled as neutral

Barplot of sentiment types

```{r sentimentBarplot}
neutral <- length(which(analysis$score == 0))
positive <- length(which(analysis$score > 0))
negative <- length(which(analysis$score < 0))
Sentiment <- c("Positive","Neutral","Negative")
Count <- c(positive,neutral,negative)
output <- data.frame(Sentiment,Count)
output$Sentiment<-factor(output$Sentiment,levels=Sentiment)
ggplot(output, aes(x=Sentiment,y=Count))+
  geom_bar(stat = "identity", aes(fill = Sentiment))+
  ggtitle("Barplot of Sentiment type of 5000 tweets")
```

Analysis: Majority of the airbnb related tweets are neutral. Positive tweets outweigh the negative tweets but not by a huge margin. There is a less than 500 tweet difference between the two amounts.

Create a word cloud

```{r wordCloud}
text_corpus <- Corpus(VectorSource(cleanText))
text_corpus <- tm_map(text_corpus, content_transformer(tolower))
text_corpus <- tm_map(text_corpus, function(x)removeWords(x,stopwords("english")))
text_corpus <- tm_map(text_corpus, removeWords, c("airbnb", "get", "got", "can"))
tdm <- TermDocumentMatrix(text_corpus)
memory.limit(15000)
tdm <- as.matrix(tdm)
tdm <- sort(rowSums(tdm), decreasing = TRUE)
tdm <- data.frame(word = names(tdm), freq = tdm)
set.seed(123)
wordcloud(text_corpus, min.freq = 1, max.words = 100, scale = c(2.2,1),
          colors=brewer.pal(8, "Dark2"), random.color = T, random.order = F)
```

Create a word frequency chart

```{r wordFrequency}
ggplot(tdm[1:20,], aes(x=reorder(word, freq), y=freq)) + 
  geom_bar(stat="identity") +
  xlab("Terms") + 
  ylab("Count") + 
  coord_flip() +
  theme(axis.text=element_text(size=7)) +
  ggtitle('Most common words related to Airbnb tweets') +
  ggeasy::easy_center_title()
```

Add sentiment scores to the original dataframe and export the csv file that will be loaded into the PowerBI dashboard.

```{r exportData}
abnbtweets <- tweets.df

abnbtweets$text <- clean.text(abnbtweets$text)

#remote empty rows
abnbtweets <- abnbtweets %>%
  filter(abnbtweets$text != " ")

# calculate and add sentiment score to dataframe
abnbtweets$score <- score.sentiment(abnbtweets$text, pos.words, neg.words)

# export data file
write.csv(abnbtweets,"AirbnbTweetsSentiment.csv")
```